Meet the team

### 2025-05-14 team.qmd
update team page

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Maria Alex </h4>
  <p> Undergraduate Research Assistant </p>
  <p> McMaster Institute for Research on Aging 2025 Summer Research Fellowship Winner </p>
  </div>
</div>

>>>>

<div class="team-member">
  <img src="images/maria-alex.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Maria Alex </h4>
  <p> Undergraduate Research Assistant </p>
  <p> McMaster Institute for Research on Aging 2025 Summer Research Fellowship Winner </p>
  </div>
</div>
